---
output:
  md_document:
    variant: markdown_github
---

# Purpose

The walk-through of how each questioned is tackled is presented below.


# Folder set-up
The code below creates the folder structure that guides the workflow of the practical.

```{r, eval = F}
CHOSEN_LOCATION <- "/Users/liezljansenvanrensburg/Desktop/data science/25424971"
fmxdat::make_project(Mac = TRUE, Open = FALSE)

Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}/"), template_name = "25424971Question1")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}/"), template_name = "25424971Question2")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}/"), template_name = "25424971Question3")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}/"), template_name = "25424971Question4")
```

# Question 1: Coffee
This sections explores the potential coffee distributors for a coffee shop in Stellenbosch. The cost (in USD), the roaster company, the roast strength, ratings, and reviews of the coffees are considered. Ulitimately, A supplier, Kakalove Cafe, is recommended

The code below loads the packages and the data. "United States and Floyd" will now fall under United States.

```{r}

if(!require ( "pacman" , quietly = TRUE ) ) {
   install.packages("pacman")
   library(pacman)
   }

pacman::p_load(purrr, lubridate, tidymodels, ggridges, ggthemes, readxl, tidyverse, lubridate, zoo, pwt10,janitor, ggsci)

list.files('25424971Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

coffee_data <- read.csv("25424971Question1/data/Coffee/Coffee.csv") %>% 
    clean_names() %>%
    mutate(
    loc_country = case_when(
      str_detect(loc_country, regex("united states", ignore_case = TRUE)) ~ "United States",
      TRUE ~ loc_country
    )
  ) %>%
  mutate(roast = na_if(roast, "")) %>%
  drop_na(roast)

```

## Average Rating and Price
### Average Rating and Price by Roaster Location
The plot below indicates that Australia and England are clear outliers. Although roasters in these countries have, on average, the highest ratings, all the countries receive an average rating of 90 or above. I would suggest that the prices disqualify the further consideration of Australian and English roasters.

```{r,  warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7}
g <-
    plot_rating_vs_price(data = coffee_data, group_var = loc_country, title = "Average Rating and Price by Roaster Country")
    
g

```

### Average Rating and Price by Roaster Location, excluding Outliers
Ratings cluster between 92 and 94, however, outliers in price remain.

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7 }

coffee_filtered <- coffee_data %>% 
    filter(!loc_country %in% c("Australia", "England"))
g <- plot_rating_vs_price(data = coffee_filtered, group_var = loc_country, title = "Average Rating and Price by Location of Roaster without Outliers")
    
g
```

### Average Rating and Price by Roast Level 
I now want to look at the relationship between roast, cost, and rating. I see that some (15) observations dont have a roast category, so Ill go back and remove blanks from the original dataframe (coffee_data). Cost and Rating have no blanks or missing values.

I see that I can just go back and adapt my function so that I can specify how I should group and then I can use the function to visualise the relationship between roast, price, and country. I actually am understanding the use of functions now!

Light roast has the highest average rating, but also the highest average cost. Dark has the lowest average rating and the lowest cost. Medium-light and medium roast offer a middle-ground.

```{r}
coffee_filtered %>% distinct(roast)

coffee_data %>%
  summarise(
    across(c(roast, cost_per_100g, rating), 
           list(n_na = ~sum(is.na(.)),
                n_blank = ~sum(. == "", na.rm = TRUE)))
  )

```

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7}
k <-
    plot_rating_vs_price(data = coffee_filtered, group_var = roast, title = "Average Rating and Price by Roast Level")
    
k
```

## Indicator words
I now want to do something with the indicator words. I like sweet, chocolate, and aroma (most used and not filler - like cup). I'll use pivot longer to create a "review" column that holds all three description columns. From there I want to see which observations have one or more of the chosen indicator words. I specify chocolate as "chocolat" so that different forms of the word is included. 

I first just filtered to the reviews that include the indicator words, but I want to add a column to show which words are included so that I can do some analysis on that potentially. This took some time to figure out what looks right, but now I am happy with the wrangling function. Now I have a matched_words column that shows which indicator words are included in the review and only the observations that have any of these words are kept.

Wrangle the data using a function:

```{r}
coffee_indicators <- extract_indicator_words(data = coffee_filtered)

head(coffee_indicators, 10)

# wow, that actually worked
```

### Average Rating and Price by Review Indicator Words
This plot indicates that coffee brands that have reviews describing the aroma and chocolatiness of the coffee are the best deal when it comes to the ratings-price relationship. Subsequent analysis will be focused on these observations.

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7}
g <-
    plot_rating_vs_price(data = coffee_indicators, group_var = matched_words, title = "Average Rating and Price by Review Indicator Words")
    
g

```

### Boxplot by Country and Roast Level
The goal is to trim the most expensive coffee products (this is informed by the subsequent analysis). Boxplot shows the outliers in red. The boxplot also illustrates that Taiwan and the US are the have the most roasters.

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7}

d <- plot_cost_boxplot(data = coffee_indicators)
d

```

### Price Distribution
The distribution in price aids in determining where a hard cap on the price should be. At USD8 per 100 grams, there is a fall in the number of coffee products sold at this price, and provides a reasonable cap.

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7,}

d <- plot_cost_distribution(data = coffee_indicators, cutoff = 8)
d
```

### Tile Plot
I have 4 variables that I now want to visualise 4 variables: roaster, roast, cost, and rating.The tile graph will have rating, roaster, and roast. I start with a new function that filters to the observations that have aroma and chocolate indicator words in their reviews. This then gets passed to a ggplot to make a tile graph. I need to calculate a midpoint for the graph, so I do that before the tile plot code. I see that I have to pull the midpoint otherwise it is a dataframe and there are issues later on. I then just do the tile plot code like I practised. I'm sure I can improve the functionality to make it more generic, but this will do for now.

There are still way too many roasters. I should go back and use price distributions to decide on a cutoff price. 

I have decided on USD8 as the cutoff price and now I can use the tile graph. It is still very cramped, so I'm going to adjust the text settings and see if that looks good. There are still too many roasters. I am only going to look at roasters that have more than one roast level, so that the supplier offers a diversified range of coffee. I will just group and ungroup to filter this in the function code.

This plot depicts the average ratings by roaster and roast level once the coffee products that have a cost larger than USD8 and roasters that only supply one remaining product have been filtered out. The reasoning is that a distributor can provide a diversified selection of products.

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7}

f <- plot_choc_aroma_tile(data = coffee_indicators)
f

```


### Prices and Ratings for Roasters
The plot below displays the price-ratings relationship for narrowd-down roasters. Kakalove Cafe seems to be a promising supplier, with most of its product prices falling the lowest, and receiving the highest some of the highest ratings. They also produce a variety of products. 

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7}

f <- plot_choc_aroma_scatter(data = coffee_indicators)
f

```

# Question 2:

```{r setup}
# set up
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require ( "pacman" , quietly = TRUE ) ) {
   install.packages("pacman")
   library(pacman)
   }

pacman::p_load(purrr, lubridate, tidymodels, ggridges, ggthemes, readxl, tidyverse, lubridate, zoo, pwt10,janitor, ggsci, haven)

list.files('25424971Question2/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))



# load data
baby_names <- read_rds("25424971Question2/data/US_Baby_names/Baby_Names_By_US_State.rds") %>% 
    clean_names
top_100 <- read_rds("25424971Question2/data/US_Baby_names/charts.rds") %>% 
    clean_names
hbo_titles <- read_rds("25424971Question2/data/US_Baby_names/HBO_titles.rds") %>% 
    clean_names
hbo_credits <- read_rds("25424971Question2/data/US_Baby_names/HBO_credits.rds") %>% 
    clean_names

```

## Introduction
This report explores the persistence in baby name trends, as well as the potential influence of popular culture on these trends.

### Spearman Rank Correlation
I like the idea of state-level data (especially New York), but for this process, I will aggregate to a national level through the national ranked function.  I will get the top 25 most popular for girls and boys. I will look at t, t+1, t+2, and t+3.

After I aggregate, I use the rank function, but this has assigned the largest rank to the most popular name (need the opposite). To get to the top 25, I just filter rank to be smaller or equal to 25 (shamefully, took me a while to figure out).

To compute the Spearman correlation, I define base year and future year objects in the function and then combine them to calculate the correlation between the rankings of these years using the Spearman method. The spearman results function expands over all the years (until 2011, as 3 future periods from then is 2014) and 1 to 3 lags are chosen, as specified in the instructions. The variable correlation is now all the spearman correlations across the years, genders, and lag lengths. For the plot, new variables are created that are used as labels. Have to make the lag variable a factor in order to apply my favourite palette. I use the facet wrap so that I can view what is happening to girls' and boys' names separately. 

```{r}
national_ranked <- get_national_ranked(baby_names)
top_25_names           <- get_top_25_names(national_ranked)
spearman_results <- get_spearman_results(top_25_names, national_ranked)
```

The time-series representations below depict the rank correlations of baby names in the US from 1910-2014. It seems that boy names are more persistent than girls names. It does appear that after the 1990's, names become less persistent, with the correlations becoming smaller. The persistence in name trends has fallen for both girl and boy names over time, however, trends seem to persistent longer still for boy names.

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7}

g <- plot_spearman_trends(spearman_results)
g
```



### Surges in Names
I want to make a function that spits out the names that have surged in popularity over the course of a year. I create the variables to calculate the year-on-year change in the number of children with each name. I need to determine what percentage would classify as a surge. After toggling it, I have chosen a threshold of 5000% for reporting. I choose to look into "Mallory". The function to create the graph is simple, but I want to spruce it up a bit. I add a line to show when "Family Ties" premiered.

Only 24% of the names have experienced a year-on-year surge greater than 5000% between 1910-2014 are boy names. The plot below inspects the popularity of the name "Mallory" over time. "Mallory" spiked in 1983 following the 1982 premiere of "Family Ties" that included the character, Mallory Keaton. It's popularity dulled over the years, illustrating the influence of popular culture on baby names.

```{r, include=FALSE}
name_surges <- get_surges(national_ranked)

```

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7}
b <- plot_name_trend(national_ranked, "Mallory")
b

```


### Name Trends: Jude
Inspired by the Beatles documentary, "Get Back", I want to look into "Jude". It looks like it gained more popularity in the 2000s. When I think of the name, I think of Jude Law. I'll see if he is credited and when his breakout roles were (The Talented Mr Ripley was released in 1999). 

According to the Billbord Hot 100, The Beatles's hit song, "Hey Jude", was charting for 19 weeks between 1968 and 1969. Further, the credits for popular films reveal that Jude Law stardom may also drive interest in this gender neutral name. These two case studies depict the impact of the media in naming conventions

```{r, warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 7}

b <- plot_name_jude(national_ranked, "Jude")
b

```

## Conclusion
Baby name trends are increasingly less persistent. This means that toy names must quickly adapt, especially those marketed towards girls. To stay on top of the trends, popular media must be studied. Through analysing song charts and IMDb ratings, the company can stay inline with the curve.  

