---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "The Persistence of and Influences on Baby Names"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "25424971"  # First Author - note the thanks message displayed as an italic footnote of first page.
#Ref1: "Satrix, Cape Town" # First Author's Affiliation
Email1: "25424971\\@sun.ac.za" # First Author's Email address

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
#RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
#Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
#abstract: |
  #This article aims to discuss what makes us happy. This is a suggested solution to question 1.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require ( "pacman" , quietly = TRUE ) ) {
   install.packages("pacman")
   library(pacman)
   }

pacman::p_load(purrr, lubridate, tidymodels, ggridges, ggthemes, readxl, tidyverse, lubridate, zoo, pwt10,janitor, ggsci, haven)

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
# load data
baby_names <- read_rds("data/US_Baby_names/Baby_Names_By_US_State.rds") %>% 
    clean_names
top_100 <- read_rds("data/US_Baby_names/charts.rds") %>% 
    clean_names
hbo_titles <- read_rds("data/US_Baby_names/HBO_titles.rds") %>% 
    clean_names
hbo_credits <- read_rds("data/US_Baby_names/HBO_credits.rds") %>% 
    clean_names
national_ranked <- get_national_ranked(baby_names)
top_25_names           <- get_top_25_names(national_ranked)
spearman_results <- get_spearman_results(top_25_names, national_ranked)

```

# Introduction
This report explores the persistence in baby name trends, as well as the potential influence of popular culture on these trends. This informs the factors that should be considered when aming characters of children's toys

## Spearman Rank Correlation
The time-series representations below depict the rank correlations of baby names in the US from 1910-2014. It seems that boy names are more persistent than girls names. It does appear that after the 1990's, names become less persistent, with the correlations becoming smaller. The persistence in name trends has fallen for both girl and boy names over time, however, trends seem to persistent longer still for boy names.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Spearman Rank Correlation.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

g <- plot_spearman_trends(spearman_results)
g
```


## Surges in Names
Only 24% of the names have experienced a year-on-year surge greater than 5000% between 1910-2014 are boy names. The plot below inspects the popularity of the name "Mallory" over time. "Mallory" spiked in 1983 following the 1982 premiere of "Family Ties" that included the character, Mallory Keaton. It's popularity dulled over the years, illustrating the influence of popular culture on baby names.

```{r, include=FALSE}
name_surges <- get_surges(national_ranked)

```

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Mallory Popularity Over Time.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
b <- plot_name_trend(national_ranked, "Mallory")
b

```

## Name Trends: Jude
According to the Billbord Hot 100, The Beatles's hit song, "Hey Jude", was charting for 19 weeks between 1968 and 1969. Further, the credits for popular films reveal that Jude Law stardom may also drive interest in this gender neutral name. These two case studies depict the impact of the media in naming conventions

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Jude Popularity Over Time.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

b <- plot_name_jude(national_ranked, "Jude")
b

```

# Conclusion
Baby name trends are increasingly less persistent. This means that toy names must quickly adapt, especially those marketed towards girls. To stay on top of the trends, popular media must be studied. Through analysing song charts and IMDb ratings, the company can stay inline with the curve.  



