---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Coffe Hub"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "25424971"  # First Author - note the thanks message displayed as an italic footnote of first page.
#Ref1: "Satrix, Cape Town" # First Author's Affiliation
Email1: "25424971\\@sun.ac.za" # First Author's Email address

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
#RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
#Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
#abstract: |
  #This article aims to discuss what makes us happy. This is a suggested solution to question 1.
---

# Introduction 
This section explores the potential coffee distributors for a coffee shop in Stellenbosch. The cost (in USD), the roaster company, the roast strength, and reviews of the coffees are considered.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require ( "pacman" , quietly = TRUE ) ) {
   install.packages("pacman")
   library(pacman)
   }

pacman::p_load(purrr, lubridate, tidymodels, ggridges, ggthemes, readxl, tidyverse, lubridate, zoo, pwt10,janitor, ggsci)

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

coffee_data <- read.csv("data/Coffee/Coffee.csv") %>% 
    clean_names() %>%
    mutate(
    loc_country = case_when(
      str_detect(loc_country, regex("united states", ignore_case = TRUE)) ~ "United States",
      TRUE ~ loc_country
    )
  ) %>%
  mutate(roast = na_if(roast, "")) %>%
  drop_na(roast)



```


```{r, include=FALSE}
coffee_data %>% 
    distinct(loc_country)

head(coffee_data, 10)

```

# Average Rating and Price
## Average Rating and Price by Roaster Location
The plot below indicates that Australia and England are clear outliers. Although roasters in these countries have, on average, the highest ratings, all the countries receive an average rating of 90 or above. I would suggest that the prices disqualify the further consideration of Australian and English roasters.

```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Average Rating and Price by Roaster Country.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
g <-
    plot_rating_vs_price(data = coffee_data, group_var = loc_country, title = "Average Rating and Price by Roaster Country")
    
g

```

## Average Rating and Price by Roaster Location, excluding Outliers
Ratings cluster between 92 and 94, however, outliers in price remain.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Average Rating and Price by Location of Roaster without Outliers.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7 }

coffee_filtered <- coffee_data %>% 
    filter(!loc_country %in% c("Australia", "England"))
g <- plot_rating_vs_price(data = coffee_filtered, group_var = loc_country, title = "Average Rating and Price by Location of Roaster without Outliers")
    
g
```

## Average Rating and Price by Roast Level 
Light roast has the highest average rating, but also the highest average cost. Dark has the lowest average rating and the lowest cost. Medium-light and medium roast offer a middle-ground.

```{r, include=FALSE}
coffee_filtered %>% distinct(roast)

coffee_data %>%
  summarise(
    across(c(roast, cost_per_100g, rating), 
           list(n_na = ~sum(is.na(.)),
                n_blank = ~sum(. == "", na.rm = TRUE)))
  )

```

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Average Rating and Price by Roast Level.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
k <-
    plot_rating_vs_price(data = coffee_filtered, group_var = roast, title = "Average Rating and Price by Roast Level")
    
k
```

# Indicator words

Wrangle the data using a function:

```{r, include=FALSE}
coffee_indicators <- extract_indicator_words(data = coffee_filtered)

head(coffee_indicators, 10)

# wow, that actually worked
```

## Average Rating and Price by Review Indicator Words
This plot indicates that coffee brands that have reviews describing the aroma and chocolatiness of the coffee are the best deal when it comes to the ratings-price relationship. Subsequent analysis will be focused on these observations.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Average Rating and Price by Review Indicator Words.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
g <-
    plot_rating_vs_price(data = coffee_indicators, group_var = matched_words, title = "Average Rating and Price by Review Indicator Words")
    
g

```
## Boxplot by Country and Roast Level
The goal is to trim the most expensive coffee products. Boxplot shows the outliers in red. The boxplot also illustrates that Taiwan and the US are the have the most roasters.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Price by Country and Roast level.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

d <- plot_cost_boxplot(data = coffee_indicators)
d

```
## Price Distribution
The distribution in price aids in determining where a hard cap on the price should be. At USD8 per 100 grams, there is a fall in the number of coffee products sold at this price, and provides a reasonable cap.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Price Distribution.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7,}

d <- plot_cost_distribution(data = coffee_indicators, cutoff = 8)
d
```


## Tile Plot
This plot depicts the average ratings by roaster and roast level once the coffee products that have a cost larger than USD8 and roasters that only supply one remaining product have been filtered out. The reasoning is that a distributor can provide a diversified selction of products.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Average Rating by Roaster and Roast Level.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

f <- plot_choc_aroma_tile(data = coffee_indicators)
f

```
## Prices and Ratings for Roasters
The plot below displays the price-ratings relationship for narrowd-down roasters. Kakalove Cafe seems to be a promising supplier, with most of its product prices falling the lowest, and receiving the highest some of the highest ratings. They also produce a variety of products. 

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Ultimate Prices and Ratings.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

f <- plot_choc_aroma_scatter(data = coffee_indicators)
f

```



