---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "What makes us happy?"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Nico Katzke^[__Contributions:__  \\newline _The authors would like to thank the World Happiness survey for showing us what happiness is._]"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Satrix, Cape Town" # First Author's Affiliation
Email1: "nfkatzke\\@gmail.com" # First Author's Email address

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  This article aims to discuss what makes us happy. This is a suggested solution to question 3.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require ( "pacman" , quietly = TRUE ) ) {
   install.packages("pacman")
   library(pacman)
}

if(!require ( "stargazer" , quietly = TRUE ) ) {
   install.packages("stargazer")
   library(stargazer)
   }

pacman::p_load(purrr, lubridate, tidymodels, ggridges, ggthemes, readxl, tidyverse, lubridate, zoo, pwt10,janitor, ggsci, haven, knitr)

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))


```

```{r}
loan_credit <- read_rds("data/Loan_Cred/loan_data.rds")
```





<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

New category variables are created and the dataframe is simplified.

```{r}
loan_clean <- get_clean_loans(loan_credit)
loan_resolved <- make_loan_resolved(loan_clean)
```

## Key Risk Drivers for Default

Inspecting the hypothesised key drivers.

```{r}
loan_resolved %>% 
    select(verification_status, dti, credit_age_yrs, 
           pub_rec_bankruptcies, pct_tl_nvr_dlq, 
           mort_acc, bc_util, num_rev_accts) %>% 
    summary()
```

```{r}
logit_model_1 <- glm(concluded_loan ~ verification_status + dti + credit_age_yrs +
                       pub_rec_bankruptcies + pct_tl_nvr_dlq + 
                       mort_acc + bc_util + num_rev_accts,
                   data   = loan_resolved,
                   family = binomial(link = "logit"))

summary(logit_model)

logit_model_2 <- glm(concluded_loan ~ verification_status + dti + credit_age_yrs +
                         pub_rec_bankruptcies + pct_tl_nvr_dlq + 
                         mort_acc + bc_util + num_rev_accts +
                         grade + int_rate + term,
                     data   = loan_resolved,
                     family = binomial(link = "logit"))

summary(logit_model_2)
```

### Results
Across both specifications, all the coefficients are statistically significant, justifying their statuses as key drivers of default risk. The Lending Club's credit grade system proves to be great indicator of debt default, with lower grades being associated with an increased probability of default. The DTI ratio, prior bankruptcies, and bankcard utilisation are also associated with increased default risk. The number of mortgage accounts and never having missed payments on debt are associated with lower default risk. 

```{r, warning =  FALSE}
stargazer(logit_model_1, logit_model_2,
          type        = "text",           # use "html" if outputting to HTML Rmd
          title       = "Logistic Regression: Predictors of Loan Default",
          dep.var.labels = "Default (1 = Loss, 0 = Paid)",
          covariate.labels = c("Source Verified", "Verified",
                               "DTI", "Credit Age",
                               "Prior Bankruptcies", "% Never Delinquent",
                               "Mortgage Accounts", "Bankcard Utilisation",
                               "No. Revolving Accounts",
                               "Grade B", "Grade C", "Grade D",
                               "Grade E", "Grade F", "Grade G",
                               "Interest Rate", "Term"),
          #apply.coef  = exp,              # shows odds ratios instead of log-odds
          p.auto      = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          no.space    = TRUE)
```

## Customers most likely to default on their debt

### By grade

The plot below illustrates that default rates increase as credit grades worsen. Customers that are assigned poor Lending Club credit grades are at higher risk of defaulting on their debt.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


d <- plot_default_by_group(loan_resolved, grade,
                      title   = "Default Rate by Credit Grade",
                      x_label = "Credit Grade")
d

```


### Home ownership


```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


d <- plot_default_by_group(loan_resolved, home_ownership,
                      title   = "Default Rate by Home Ownership",
                      x_label = "Home Ownership"
                      )
d

```

### Employment length

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <- plot_default_by_group(loan_resolved, emp_length,
                      title   = "Default Rate by Employment Length",
                      x_label = "Employment Length")
                      
c

```


### State

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <-  plot_default_by_state(loan_resolved)
                      
c

```


### Purpose

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <- plot_default_by_group(loan_resolved, purpose,
                      title   = "Default Rate by Purpose of Debt",
                      x_label = "Purpose")
                      
c

```



### DTI

#### DTI by outcome

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <-  plot_dti_by_outcome(loan_clean)
                      
c
```
#### DTI bins
```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <-  table_dti_hardcap(loan_resolved)
                      
c
```



## Heuristics - State in st


```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <-  ST_plot_default_by_state(loan_resolved)
                      
c

```



<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

