---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Loans and Credit"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "25424971"  # First Author - note the thanks message displayed as an italic footnote of first page.
#Ref1: "Satrix, Cape Town" # First Author's Affiliation
Email1: "25424971\\@sun.ac.za" # First Author's Email address

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
#RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
#Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
#abstract: |
  #This article aims to discuss what makes us happy. This is a suggested solution to question 1.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require ( "pacman" , quietly = TRUE ) ) {
   install.packages("pacman")
   library(pacman)
}

if(!require ( "stargazer" , quietly = TRUE ) ) {
   install.packages("stargazer")
   library(stargazer)
   }

pacman::p_load(purrr, lubridate, tidymodels, ggridges, ggthemes, readxl, tidyverse, lubridate, zoo, pwt10,janitor, ggsci, haven, knitr)

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

loan_credit <- read_rds("data/Loan_Cred/loan_data.rds")

# New category variables are created and the dataframe is simplified.
loan_clean <- get_clean_loans(loan_credit)
loan_resolved <- make_loan_resolved(loan_clean)
```

# Introduction 
The key drivers of default risk are explored. The following factors of individuals are considered: whether the income source was verified, the debt-to-income ratio, the number of year that the individual has had any sort of credit line, prior bankruptcies, the number of mortgage accounts, bankcard utilisation,  interest rate, term length, and history of credit behaviour.

## The Key Risk Drivers for Default
A logistic regression is used to study the determinants of default risk, as the dependent variable is binary in nature. 
Across both specifications, all the coefficients are statistically significant, justifying their statuses as key drivers of default risk. The Lending Club's credit grade system proves to be great indicator of debt default, with lower grades being associated with an increased probability of default. The DTI ratio, prior bankruptcies, and bankcard utilisation are also associated with increased default risk. The number of mortgage accounts and never having missed payments on debt are associated with lower default risk. 


```{r, include=FALSE}
loan_resolved %>% 
    select(verification_status, dti, credit_age_yrs, 
           pub_rec_bankruptcies, pct_tl_nvr_dlq, 
           mort_acc, bc_util, num_rev_accts) %>% 
    summary()
```

```{r, include=FALSE}
logit_model_1 <- glm(concluded_loan ~ verification_status + dti + credit_age_yrs +
                       pub_rec_bankruptcies + pct_tl_nvr_dlq + 
                       mort_acc + bc_util + num_rev_accts,
                   data   = loan_resolved,
                   family = binomial(link = "logit"))

summary(logit_model_1)

logit_model_2 <- glm(concluded_loan ~ verification_status + dti + credit_age_yrs +
                         pub_rec_bankruptcies + pct_tl_nvr_dlq + 
                         mort_acc + bc_util + num_rev_accts +
                         grade + int_rate + term,
                     data   = loan_resolved,
                     family = binomial(link = "logit"))

summary(logit_model_2)
```


```{r, warning =  FALSE}
stargazer(logit_model_1, logit_model_2,
          type        = "text",           
          title       = "Logistic Regression: Predictors of Loan Default",
          dep.var.labels = "Default (1 = Loss, 0 = Paid)",
          covariate.labels = c("Source Verified", "Verified",
                               "DTI", "Credit Age",
                               "Prior Bankruptcies", "% Never Delinquent",
                               "Mortgage Accounts", "Bankcard Utilisation",
                               "No. Revolving Accounts",
                               "Grade B", "Grade C", "Grade D",
                               "Grade E", "Grade F", "Grade G",
                               "Interest Rate", "Term"),
       
          p.auto      = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          no.space    = TRUE)
```

## Default-Risk Customer Profiles

### Default Rate by Lending Club’s Customer Grading System 

The plot below illustrates that default rates increase as credit grades worsen. Customers that are assigned poor Lending Club credit grades are at higher risk of defaulting on their debt.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Default Rate by Grading System .\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


d <- plot_default_by_group(loan_resolved, grade,
                      title   = "Default Rate by Credit Grade",
                      x_label = "Credit Grade")
d

```

### Default Rate by Home Ownership
Individuals that rent instead of own their house/mortgage have an average default rate of 26.9%. Owning a mortgage is associated with the lowest average default rate, supporting the findings of the logit regression, where the number of mortgages negatively relates to the default rate. This may simply be a proxy for income.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Default Rate by Home Ownership.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


d <- plot_default_by_group(loan_resolved, home_ownership,
                      title   = "Default Rate by Home Ownership",
                      x_label = "Home Ownership"
                      )
d

```

### Default Rate by Employment Length
The default rate appers to be similarly distributed across employment lengths, with a slight downward trend, such that longer employment years (stable income) indicate a slightly lower risk of default. 

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Default Rate by Employment Length.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <- plot_default_by_group(loan_resolved, emp_length,
                      title   = "Default Rate by Employment Length",
                      x_label = "Employment Length")
                      
c

```


### Default Rate by State for Both Long and Short Term Loans
Arkansas, Los Angeles, Mississipi, Nebraska, and Oklahoma have the highest average default rates, signalling that individuals from these states iintroduce increased risk. Whereas individuals from DC, Maine, New Hampshire, Oregan, Vermont, and West Virginia signal prudence, as these states have the lowest average default rates.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Default Rate by State for Both Long and Short Term Loans.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <-  plot_default_by_state(loan_resolved)
                      
c

```

### Default Rate by State for Short Term Loans Only
The state analysis is similar when only short-term loans are considered.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Default Rate by State for Short Term Loans Only.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <-  ST_plot_default_by_state(loan_resolved)
                      
c

```

### Default Rate by Purpose of Loan
Individuals who cite funding a small business or planning a wedding as the reason for their debt obligations are at the highest risk of defaulting on their loans.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Default Rate by Purpose.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <- plot_default_by_group(loan_resolved, purpose,
                      title   = "Default Rate by Purpose of Debt",
                      x_label = "Purpose")
                      
c

```

## The Debt-to-Income and Loan Status Relationship
The average debt-to-income ratio is the highest for those who have defaulted on their loans and completely written their loans off, although the variance is not large across these broader loan status groups.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Average DTI by Loan Status.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}


c <-  plot_dti_by_outcome(loan_clean)
                      
c
```
# Conclusion
Multiple factors must be considered when approving loan applications to ensure that the default rate is minimised. By scrutinizing over where individuals reside, the debt-to-income ratios, the purpose of the credit, the credit category, home ownership, length of employment, debt history, and bankcard utilisation, debt default risk can be improved.




