---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Streaming Platform Investigation"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "25424971"  # First Author - note the thanks message displayed as an italic footnote of first page.
#Ref1: "Satrix, Cape Town" # First Author's Affiliation
Email1: "25424971\\@sun.ac.za" # First Author's Email address

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
#RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
#Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
#abstract: |
  #This article aims to discuss what makes us happy. This is a suggested solution to question 1.
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require ( "pacman" , quietly = TRUE ) ) {
   install.packages("pacman")
   library(pacman)
   }

pacman::p_load(purrr, lubridate, tidymodels, ggridges, ggthemes, readxl, tidyverse, lubridate, zoo, pwt10,janitor, ggsci, haven)

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

# data load
titles <- read_rds("data/netflix/titles.rds")
credits <- read_rds("data/netflix/credits.rds")
movie_info <- read_csv("data/netflix/netflix_movies.csv")
```

# Introduction 
The genre, ratings, country of production, and film length are factors that determine which movies should be hosted on an up-and-coming streaming site.

## IMDb Scores by Genre
IMDb score density plots reveal that critics ratings are the highest amongst documentaries, historical, and war films, motivating the prioritisation of these genres for the streaming site. Horror films have the flattest distribution, indicating that care should be taken when selecting films from these genres.

```{r, include=FALSE}
titles %>% count(type)

titles %>% 
  select(genres, production_countries) %>% 
  head(10)

titles %>% 
  summarise(
    na_score    = sum(is.na(imdb_score)),
    na_runtime  = sum(is.na(runtime)),
    na_genres   = sum(is.na(genres)),
    na_country  = sum(is.na(production_countries)),
    na_year     = sum(is.na(release_year))
  )
```
```{r}
movies <- clean_movies(titles)
movies_long <- make_movies_long(movies)
```

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "IMDb Scores by Genre.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
w <- plot_genre_ridges(movies_long, 
                  score_var = imdb_score, 
                  title     = "IMDb Scores by Genre", 
                  x_axis    = "IMDb Score")
w
```
## User Scores by Genre
The reality genre of films might have the highest median user rating, but the distribution is trimodal, indictaing that films should be carefully selected. Further, music, hictoric, and documentary films are highly rated amongst users. Since users will be the predominant viewers on the streaming site, more credence should be given to their preferences

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "User Scores by Genre.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
w <- plot_genre_ridges(movies_long, 
                  score_var = tmdb_score, 
                  title     = "User Scores by Genre", 
                  x_axis    = "TMDB Score")
w
```

## Popularity, Ratings, and Runtime
A negative relationship exists between IMDb ratings and popularity scores. This illustrates how controversy drums attention - which should be kept in mind when curating a film catalog. Runtime is illustrated by the size of the bubbles. War films have a long duration and high popularity scoresa and ratings - the ideal genre.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "IMDb Score vs TMDB Popularity by Genre.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
m <- plot_score_scatter(movies,
                   x_var     = imdb_score,
                   y_var     = tmdb_popularity,
                   size_var  = runtime,
                   label_var = primary_genre,
                   title     = "IMDb Score vs TMDB Popularity by Genre",
                   x_axis    = "Avg IMDb Score",
                   y_axis    = "Avg TMDB Popularity")
m
```

## Tile Plot of Average Rating by Country and Genre
Films primarily produced in the Phillipines in the crime, drama, science fiction and European genres have the highest average ratings. These films should be prioritised. Romance films produced in Turkey also receive high praise. Films produced in Nigeria should be avoided and Mexican films should be carefully selected to fall within the comedy and crime genres.

```{r, warning =  FALSE, fig.align = 'center', fig.cap = "Average Rating by Country and Genre.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
m <- plot_country_genre_heatmap(movies_long)
m
```

# Conclusion
Across the board, war fims and documentaries should be prioritised, while popular - potentially controversial - films should be promoted to stimulate interest in the streaming site. The country of production should be considered when curating the films, as this potentially serves as a proxy for quality and impacts ratings.
